Manuscript Figures

### 2021-09-13 src/manuscript_figures.Rmd
add jonas tmz gbm analysis figures

>>>>

```{r tmz_gbm}
# TMZ resistance in GBM anaysis by Jona.
# Here I import figure data to have consistent figure styles
folder <- '/data/local/buyar/arcas/pancancer_multiomics_manuscript/results/tmz_gbm_jona'

# cross-validation results predicting TMZ resistance using 
# maui LFs and other known markers 
aucs <- data.table::fread(file.path(folder, 'aucs.csv'))
aucs$group <- ifelse(grepl('LF', aucs$method), 'maui', 'no-maui')
aucs$method <- gsub("LF[Ss]", "MAUI LFs", aucs$method)
colnames(aucs)[2] <- c('AUC')
Fig <- ggpubr::ggbarplot(aucs, x = 'method', y = 'AUC', add = 'mean_se',
                  fill = 'group') +
  theme(axis.title.x = element_blank(), legend.position = 'none', 
        ) + 
  scale_fill_brewer(type = 'qual', palette = 3)

fig_count <- fig_count + 1
Figures[[fig_count]] <- Fig
fig.name <- paste0('Figure', fig_count, '.tmz_gbm.pdf')
names(Figures)[fig_count] <- fig.name
ggsave(file.path(FigureFolder, fig.name),
              plot = Fig, units = 'in', width = 10, height = 6)
Legends[[fig_count]] <- "Classification accuracy quantified as the Area under the ROC (AUC) when predicting TMZ resistance in GBM patients using MAUI LFs alone or in combination with the MGMT expression or promoter methylation values."

# supplementary figure
topGenes <- data.table::fread(file.path(folder, 'top100_genes.csv'))
colnames(topGenes)[4] <- 'literature'
topGenes$label <- 'Other'
topGenes[MMR == TRUE]$label <- 'MMR Pathway'
topGenes[literature == TRUE]$label <- 'Literature Support'

supFig <- ggpubr::ggbarplot(topGenes, x = 'V1', y = 'Gene score', 
                  fill = 'label') +
  theme(axis.title.y = element_blank(), legend.title = element_blank(),
        axis.text.y = element_text(size = 8)) +
  coord_flip()

supFig_count <- supFig_count + 1
SuppFigures[[supFig_count]] <- supFig
fig.name <- paste0('SuppFigure', supFig_count, '.tmz_gbm.supp.pdf')
names(SuppFigures)[supFig_count] <- fig.name
ggsave(file.path(FigureFolder, fig.name), 
              plot = supFig, units = 'in', width = 8.27, height = 11.69)
SuppLegends[[supFig_count]] <- "Top 100 genes sorted by importance in predicting TMZ resistance in GBM patients."
```
